Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
refactor related work section

@@

\section{Related work}\label{document:related_work}
This section will analyze three different algorithms that have been
proposed as solutions for type 2 puzzles.
The objective is to understand the strengths and weaknesses of each one,
in order to build up knowledge that will be useful for the next sections.

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
This algorithm falls within the ``binary comparison'' category~\cref{document:comparator}.
And can be used to understand the strength and weaknesses
of this approach.\newline
The primary advantage of this approach lies in its speed;
the utilization of binary comparison permits specific optimizations,
particularly leveraging graph theory techniques.\newline
The algorithm exhibits a time complexity of approximately \(O(N^2)\),
a value consistent with the theoretical minimum for
jigsaw puzzle solving, as outlined in the study
``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
However, a potential drawback may arise in terms of accuracy.
This stems from the fact that, with only two states
(matching or not matching),
certain details may be lost when compared to a non-binary comparison. 
To quantify accuracy the paper used the ``neighbors compariso'' metric,
which ``calculates the percentage of pairs of image patches that are matched correctly''.
This will be useful later.\label{document:GCL}

>>>>

\section{Related work}\label{document:related_work}
Now that we have developed our own solution, it would be
interesting to see how it compares against the current
state-of-the-art algorithms for both digital and real-world
jigsaw puzzles. This section gives a brief introduction to 3
state-of-the-art algorithms, so that they can be compared with
our solution in the conclusions.

\subsection{Solving Jigsaw Puzzles By The Graph Connection Laplacian~\cite{GCL}}
This algorithm falls within the ``binary comparison'' category (\cref{document:comparator}).
And can be used to understand the strength and weaknesses
of this approach.\newline
The primary advantage of this approach lies in its speed;
the utilization of binary comparison permits specific optimizations,
particularly leveraging graph theory techniques.\newline
The algorithm exhibits a time complexity of approximately \(O(N^2)\),
a value consistent with the theoretical minimum for
jigsaw puzzle solving, as outlined in the study
``No easy puzzles: Hardness results for jigsaw puzzles~\cite{ON2Claim}''.\newline
However, a potential drawback may arise in terms of accuracy.
This stems from the fact that, with only two states
(matching or not matching),
certain details may be lost when compared to a non-binary comparison. 
To quantify accuracy the paper used the ``neighbors compariso'' metric,
which ``calculates the percentage of pairs of image patches that are matched correctly''.
This will be useful later.\label{document:GCL}

@@
